### 2023-04-06 resilience.tex
Adding examples to sec3 for now

%%%
\iffalse
%%%%
%%%%
\subsection{Defining resilience}

\subsubsection{Resilience for general transition systems}

We ask whether we can reach a state 
%which satisfies
in 
%
$\Safe$  in a reasonable amount of time whenever we reach a state 
% which satisfies
in
%
$\Bad$. 
From this we formulate two resilience problems. First consider the case where the recovery time
is bound by a given natural number $k \geq 0$, i.e., the \emph{explicit resilience problem} for TS.

\problemx{$k$-Resilience problem }
{a transition system $(S,\rightarrow)$, an integer $k$, a state $s \in S$, $\Safe, \Bad \subseteq S$ and $\Safe \cap \Bad = \emptyset$.}
{$\forall s' \in \Bad, ~ s \rightarrow^* s' \implies \exists s'' \in \Safe ~ s' \rightarrow^{\leq k} s''$ ?\newline}

If a system $S$ satisfies the explicit resilience property for an integer $k$, we say that $S$ is $k$-resilient.

% If we assume that the transition system yields infinite sequences of transitions, we can express the property to be evaluated in CTL by s |= AG(\Bad → 0≤ j≤k EX j \Safe).

We can also ask whether there exists such a bound $k$ such that $S$ is $k$-resilient. We call this problem the \emph{bounded resilience problem}.

%
%\problemx{Bounded Resilience problem}
%{a transition system $(S,\rightarrow)$, a state $s \in S$, $\Safe, \Bad \subseteq S$ and $\Safe \cap \Bad = \emptyset$.}
%{$\exists k \geq 0 ~ \forall s' \in \Bad, ~ s \rightarrow^* s' \implies \exists s'' \in \Safe ~ s' \rightarrow^{\leq k} s''$ ?\newline}
%

\problemx{Bounded Resilience problem}
{a transition system $(S,\rightarrow)$, a state $s \in S$, $\Safe, \Bad \subseteq S$ and $\Safe \cap \Bad = \emptyset$.}
{$\exists k \geq 0  \mathscr{S}$ is $k$-resilient. ?\newline}
%%

%%%

pour $k,k'$ donnés, chercher si $\Safe_{max}$ et $\Bad_{max}$ ont un sens ? on peut faire l'union des \Safe, \Safe' et des \Bad, \Bad' prendre le max des k. Fixer k, chercher et calculer $\Safe_{max}$ et $\Bad_{max}$.

%
%\alain{dire juste que \Safe = upward closed et \Bad = downward closed.
%envisager les 3 autres cas. souvent \Bad = upward closed (par ex l'exclusion mutuelle).
%4 resilience problem (U,D), (U,U), (D,U), (D,D)}

\newcommand{\Bad}{\textsf{Bad}}
\newcommand{\Safe}{\textsf{Safe}}

@@

>>>>

@@

\begin{example}
% Avec Safe = up( q_1(3,0) ) et Bad = q_0 (N,N) on aurait la 1-résilience et donc la résilience par exemple
% mais avec Safe = up(q_0(3,0)) et Bad = q_1(N,N) on ne l'aurait pas à cause de q_1(0,0) 
Let $V = (\{q_0,q_1\}, \{ (q_0, (3,0), q_1), (q_1, (-1,1), q_0)\})$ be a vector addition system with states (VASS),
and thus a WSTS.
Case A) is $\Safe = \uparrow q_1(3,0)$ and $\Bad = \uparrow q_0(0,0)$, $1$-resilience holds.
Case B) is $\Safe = \uparrow q_0(3,0)$ and $\Bad = \uparrow q_1(0,0)$, resilience do not hold because of $q_1(0,0) \in \Bad$.
% (si on veut se rajouter une hypothèse comme pas de dead-end on peut rajouter un troisième état q_2 duquel on puisse partir depuis q_1 en faisant par exemple +1,+1 et qui loop sur lui-même) 
\end{example}

\begin{center}
	\begin{figure}
			\hspace{3.75cm}
\includegraphics[width=0.2\textwidth]{FigureA}
	\label{example_1}
	\end{figure}
\end{center}

\begin{example}
% Si on prends un Z-vass avec même seulement un compteur, Safe les entiers positifs, Bad le reste, avec juste une transition qui fait +1, alors on a la résilience (on reviens toujours dans les positifs) mais pas la bounded resilience.
$\mathds{Z}$-VASS, one counter, $\Safe = \uparrow 0$, $\Bad = \downarrow -1$, transition: $+1$,
then resilience hold but not bounded resilience. 
\end{example}
